\pkg{shorts}: An R Package for Modeling Short Sprints

### 2020-10-26 paper.Rmd
Added calculation of 99% MSS for Bolt's example

>>>>

Here is the model estimate of the time and distance it takes for Bolt to reach 99% of MSS:

```{r}
bolt_model <- bolt_model %>%
  group_by(model) %>%
  mutate(
    dist_95_MSS = find_velocity_critical_distance(
      MSS = MSS, TAU = TAU, time_correction = time_correction, 
      distance_correction = distance_correction, percent = 0.99
    ),
   time_95_MSS = find_velocity_critical_time(
      MSS = MSS, TAU = TAU, time_correction = time_correction, 
      percent = 0.99
    )
  )

bolt_model[c(1, 8, 9)]
```

### 2020-10-26 paper.tex
Added calculation of 99% MSS for Bolt's example

@@

\begin{center}\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-51-1} \end{center}

@@

>>>>

Here is the model estimate of the time and distance it takes for Bolt to reach 99\% of MSS:

\begin{CodeChunk}
\begin{CodeInput}
R> bolt_model <- bolt_model %>%
+   group_by(model) %>%
+   mutate(
+     dist_95_MSS = find_velocity_critical_distance(
+       MSS = MSS, TAU = TAU, time_correction = time_correction, 
+       distance_correction = distance_correction, percent = 0.99
+     ),
+    time_95_MSS = find_velocity_critical_time(
+       MSS = MSS, TAU = TAU, time_correction = time_correction, 
+       percent = 0.99
+     )
+   )
R> 
R> bolt_model[c(1, 8, 9)]
\end{CodeInput}
\begin{CodeOutput}
#> # A tibble: 6 x 3
#> # Groups:   model [6]
#>   model                    dist_95_MSS time_95_MSS
#>   <chr>                          <dbl>       <dbl>
#> 1 No correction                   68.7        7.20
#> 2 No correction - RT              51.1        5.73
#> 3 Time correction                 51.0        5.72
#> 4 Time correction - RT            51.0        5.54
#> 5 Distance correction             39.8        4.75
#> 6 Distance correction - RT        39.8        4.57
\end{CodeOutput}
\end{CodeChunk}

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-55-1} \end{center}
